\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
bib
Update on Overleaf.

Spiking neurons with hetero-synaptic delays for motion detection

@@

\subsection{Task definition: fast motion detection}
%
Let us now define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. For example, saccades are rapid movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average one every 3 seconds~\citep{}). They are produced very rapidly (about 80ms) and the maximum speed is proportional to the amplitude of the displacement (up to 600 deg/sec for a large saccade of 30deg amplitude). At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{Poletti 2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{Engbert 2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-velocity=7 different velocities (see inset of \seeFig{motion-task}-(a)). Note that the velocities are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Next, we define one trajectory of gaze as segments whose duration is drawn from a Poisson distribution with an average block length = 20 ms - similar to a Lévy flight~\citep{}. Finally, the trajectory is integrated by assuming 1/ that velocities are uniformly and independently sampled from the set of different motion-sets and 2/ that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for human eye movements (\seeFig{motion-task}-(a)).

@@

%Note that this supervised learning scheme can be extended to a variety of tasks. It would follow from the emergence of new kernels adapted to this new task after supervised learning.  This constitutes a major advantage over other algorithms which derive event-based algorithms from specific physical rules (see for instance~\citep{benosman_asynchronous_2012} for computing the optic flow using the luminance conservation rule). We aim at extending the application of this model on more generic datasets acquired in natural conditions for progressively more complex tasks from motion extraction, optic flow or time-to-contact maps.
%

>>>>

Learning synaptic delays of spiking neurons for motion detection

@@

\subsection{Task definition: fast motion detection}
%
Let us now define a trajectory inspired by the biological movements of the eyes. Indeed, these movements allow us to dynamically actuate the center of vision, or gaze, in the field of vision. In animals with a fovea, this is particularly useful as it allows to move the area with the highest density of photoreceptors in the environment, for example at a point of interest. For example, saccades are rapid movements of the eyeball that reposition the center of vision. In humans, these are very frequent (on average one every 3 per second~\citep{dandekar_neural_2012}). They are produced very rapidly (about $80~\ms$) and display a whole range of speeds. At a more microscopic scale, the human gaze moves with an incessant drift similar to a Brownian-like trajectory~\citep{Poletti 2015}. To maintain the full generality of the task, we will define eye movements using a form of random walk~\citep{Engbert 2011}. This approach first defines a finite set of possible 2D motions in polar coordinates. Based on the distribution of biological motions, we simplified it by selecting a set of eye movements as the Cartesian product of N-V-phi=8 linearly spaced motion directions and N-Y-velocity=7 different velocities (see inset of \seeFig{motion-task}-(a)). Note that the velocities are sampled on a geometric scale between $1/4$ and $v-speed_base = 4$. Next, we define one trajectory of gaze as segments whose duration is drawn from a Poisson distribution with an average block length = 20 ms - similar to a Lévy flight~\citep{}. Finally, the trajectory is integrated by assuming 1/ that velocities are uniformly and independently sampled from the set of different motion-sets and 2/ that motion is uniform during a time segment. The resulting instances yield trajectories qualitatively similar to those observed for human eye movements (\seeFig{motion-task}-(a)).

@@

%Note that this supervised learning scheme can be extended to a variety of tasks. It would follow from the emergence of new kernels adapted to this new task after supervised learning.  This constitutes a major advantage over other algorithms which derive event-based algorithms from specific physical rules (see for instance~\citep{benosman_asynchronous_2012} for computing the optic flow using the luminance conservation rule). We aim at extending the application of this model on more generic datasets acquired in natural conditions for progressively more complex tasks from motion extraction, optic flow or time-to-contact maps.
% >>>>>>>>>>> LuP is here <<<<<<<<<<<
